Computer Science House Constitution

### 2023-01-30 constitution.tex
normal pull request

@@

\asubsection{Qualifications to be the House Secretary or an Ad Hoc Director}
\begin{enumerate}
\item Candidates must be Active Members
\end{enumerate}

@@

@@

\asection{Term}
\begin{enumerate}
\item The Election Process for the following year's Executive Board members shall begin in the middle of Spring semester.
\item The newly selected officers shall begin their terms on June 1 of that year and their terms shall end on May 31 of the following year.
\item The term of an officer will be abbreviated due to resignation, impeachment, or change in membership status.
\item Officers elected or selected during the course of the year due to an abbreviated term of the previous officer shall hold office until the end of the normal term.
\item When the task of an Ad Hoc Directorship has been completed, the directorship dissolves.
	When an Ad Hoc Director resigns, the directorship dissolves and must be reinstated with a new director.
\end{enumerate}

>>>>

\asubsection{Responsibilities of Committees}
\begin{enumerate}
	\item Committees are responsible for the task for which they were created
	\item Any responsibilities of the Committee are placed upon the assigned Lead
\end{enumerate}

@@

\asubsection{Qualifications to be the House Secretary, an Ad Hoc Director, or a Committee Lead}
\begin{enumerate}
\item Candidates must be Active Members
\end{enumerate}

@@

\asubsection{Selection of Committee Leads}
	\item When a group of House members feels a Committee is necessary, a public declaration may be made during House Meeting, stating the purpose of the Committee.
	\item When a Committee is declared it is automatically granted status and a Lead is appointed, but all other aspects of a Committee's operation are at the Lead's discretion.
	\item When a Committee is granted status it is never granted a budget.

@@

\asection{Term}
\begin{enumerate}
\item The Election Process for the following year's Executive Board members shall begin in the middle of Spring semester.
\item The newly selected officers shall begin their terms on June 1 of that year and their terms shall end on May 31 of the following year.
\item The term of an officer will be abbreviated due to resignation, impeachment, or change in membership status.
\item Officers elected or selected during the course of the year due to an abbreviated term of the previous officer shall hold office until the end of the normal term.
\item When the task of an Ad Hoc Directorship has been completed, the directorship dissolves.
	When an Ad Hoc Director resigns, the directorship dissolves and must be reinstated with a new director.
\item When the task of a Committee has been completed, the Committee dissolves.
	A Committee may be dissolved at any time by a simple majority vote of the Executive Board.
\end{enumerate}
